Stochastic Approximation Monte Carlo with a Dynamic Update Factor

### 2019-11-09 papers/histogram/sad.tex
start intro to lj31 section

>>>>

Clusters of Lennard-Jones atoms have been frequently used for testing
Monte Carlo algorithms~\davidsays{add a few citations}.  The 31-atom
cluster is popular because it features a two-funnel energy landscape
with a significant barrier between the two low-energy
states~\davidsays{add citations}.

Poulain \emph{et al.} found \cite{poulain2006performances}
